Kindly Bent to Free Us

### 2019-07-06 kindly/lang.tex
Tiny fixes.

We illustrate this on the expression $\region{x}{f(\borrow[\IBORROW]{c})}$.
The first step is to check that
$\svar[\IBORROW]{c}{\text{channel}}$ is in $\E$. We then define $\E'$ which
corresponds to $\E$ where the suspended binding is replaced by a borrow binding.
%
This is done by the borrow relation, noted $\lregion{C}{x}{\E}{\E'}$ and
whose main rules are shown in \cref{selectrules:region}.
In our case, we consider an immutable binding, so we replace the suspended
binding by $\bvar{\borrow[\IBORROW]{c}}{\borrowty[\IBORROW]{k}{\text{channel}}}$.
We must also check that $\entail{C}{(\kun_n\lk k\lk\kun_\infty)}$.
We can then typecheck the body of the region, $f(\borrow[\IBORROW]{c})$ for our example and check that the borrow made available in the region does not escape.
This is done by the constraint $\Cleq{\tau}{\klin_{n-1}}$, which ensures
that the kind of $\tau$ does not contain anything whose kind is ``above $n$''
(for instance, $\borrowty[\IBORROW]{\kun_n}{\text{channel}}$ would have kind
$\kun_n$).

@@

>>>>

We illustrate this on the expression $\region{x}{f(\borrow[\IBORROW]{c})}$.
The first step is to check that
$\svar[\IBORROW]{c}{\text{channel}}$ is in $\E$. We then define $\E'$ which
corresponds to $\E$ where the suspended binding is replaced by a borrow binding.
%
This is done by the borrow relation, noted $\lregion{C}{x}{\E}{\E'}$ and
whose main rules are shown in \cref{selectrules:region}.
In our case, we consider an immutable binding, so we replace the suspended
binding by $\bvar{\borrow[\IBORROW]{c}}{\borrowty[\IBORROW]{k}{\text{channel}}}$.
We must also check that $\entail{C}{(\kun_n\lk k\lk\kun_\infty)}$.
We can then typecheck the body of the region, $f(\borrow[\IBORROW]{c})$ in our example, and check that the borrow made available in the region does not escape.
This is done by the constraint $\Cleq{\tau}{\klin_{n-1}}$, which ensures
that the kind of $\tau$ does not contain anything whose kind is ``above $n$''
(for instance, $\borrowty[\IBORROW]{\kun_n}{\text{channel}}$ would have kind
$\kun_n$).

@@

\subsubsection{Kind checking}

\TODO{Present this if we have enough space}

\subsubsection{Pattern matching}

\TODO{Present this if we have enough space}
